\documentclass[10pt]{article}

\input{structure.tex}
\usepackage{multicol}
\begin{document}

  \begin{paracol}{2}
    \parbox[top][0.12\textheight][c]{\linewidth}{
      \vspace{-0.04\textheight}
      \centering
      {\sffamily\Huge Ali Sorour Amini}\\\medskip
      {\Huge\color{headings}\cvtextfont Curriculum Vitae}
    }

    \switchcolumn

    \parbox[top][0.12\textheight][c]{\linewidth}{
      \vspace{-0.04\textheight}
      \colorbox{shade}{
        \begin{supertabular}{p{0.05\linewidth}|p{0.775\linewidth}}
          \raisebox{-1pt}{\faHome} & \\
          \raisebox{-1pt}{\faPhone} & +98 (939) 599-2486 \\
          \raisebox{0pt}{\small\faEnvelope} & \href{mailto:ali.sorouramini@ut.ac.ir}{ali.sorouramini@ut.ac.ir} \\
          \raisebox{-1pt}{\faGithub} & \href{https://github.com/AliSoAm}{https://github.com/AliSoAm} \\
          \raisebox{-1pt}{\faLinkedinSquare} & \href{https://www.linkedin.com/in/AliSoAm}{https://www.linkedin.com/in/AliSoAm} \\
        \end{supertabular}
      }
    }
  \end{paracol}
  \begin{paracol}{2}
    \section{Education}
      \begin{supertabular}{rl}
        \educationentry{2016 -- present}
          {Master of Science}
          {}
          {Electrical Engineering}
          {Communications Networks}
          {18.15/20~(3.77/4)}
          {}
          {University of Tehran}
        \educationentry{2008 -- 2012}
          {Bachelor of Science}
          {}
          {Electrical Engineering}
          {Communications}
          {18.22/20~(?/4)}
          {}
          {University of Tehran}
      \end{supertabular}
      \medskip
    \section{Awards}
      \begin{supertabular}{rl}
        \tableentry{2016}{\textbf{M.Sc. Fellowship Award}}{}
        \tableentry{}{Exceptional Talented Student}{}
        \tableentry{}{\textit{University of Tehran}}{spaceafter}
      \end{supertabular}
      \medskip
    \section{Research Interests}
      \begin{multicols}{2}
        \begin{itemize}
          \item Machine Learning
          \item Game Theory
          \item Distributed Algorithms
          \item Optimization
          \item Network Function Virtualization
          \item Big Data
        \end{itemize}
      \end{multicols}
      \medskip

    \section{Work Experience}
      \workposition{from Jun 2016}
      {PT}
      {ESFA Lab-University of Tehran}
      {M.Sc. student, Researcher}
      {
        Design and development of a measurement device used to identify phase id (R, S, T) of electrical system subscribers under supervision of \textbf{Dr. Mahdi Davarpanah}.
        I 
        In pilot stage 70000 subscribers has been measured.
      }
      \medskip
      \workposition{Jan 2015 -- Jan 2016}
      {PT}
      {Array Processing Lab-University of Tehran}
      {B.Sc. student, Research Assistant}
      {
        Designing and implementing a wireless communication link using SDR board based on Xilinx ZYNQ 7020 and analyzing among different modulations;
        Under supervision of \textbf{Dr. Aliazam Abbasfar}.
      }
      \vspace{-\baselineskip}
      \medskip

    \switchcolumn
    \section{Computer Skills}
      \begin{supertabular}{rl}
        \tableentry{Beginner}{}{spaceafter}
        \tableentry{Intermediate}{\LaTeX, Javascript, HTML, CSS,}{spaceafter}
        \tableentry{Expert}{C/C++, Python, Git, Linux, Matlab}{spaceafter}
      \end{supertabular}
      \medskip
    \section{Skills}
      \longformdescription{Goal Oriented}{I believe in action over long-winded discussions. I listen to everyone's viewpoints and use my judgement to immediately act based on consensus to achieve goals quickly and efficiently.}

      \longformdescription{Physical Dexterity}{Manual manipulation of experimental equipment and training within Black Mesa (e.g. the Hazard Course) have contributed to an enjoyment of working with my hands.}

      \longformdescription{Passionate}{I have been interested in theoretical physics such as quantum mechanics and relativity from an early age. My education and research have cemented this interest into a passion. I greatly enjoy carrying out fundamental physics research with potential practical applications.}
      \medskip
    \section{Publications}
      \longformpublication{\textbf{Freeman, G. R.} (1996). Chemistry of Multiply Charged Negative Molecular Ions and Clusters in the Gas Phase:  Terrestrial and in Intense Galactic Magnetic Fields. \textit{The Journal of Physical Chemistry}, \textit{100}(11), 4331-4338.}

      \medskip
    \section{References}
      \begin{supertabular}{rl}
        \tableentry{}{\textbf{Dr. Vahid Shahmansouri}}{spaceafter}
        \tableentry{Position}{Assistant Professor}{}
        \tableentry{Employer}{\href{http://ece.ut.ac.ir/}{School of Electrical and Computer Engineering}}{}
        \tableentry{}{\href{https://ut.ac.ir}{\textit{University of Tehran}}}{spaceafter}
        \tableentry{Email}{\href{mailto:vmansouri@ut.ac.ir}{vmansouri@ut.ac.ir}}{}
        \tableentry{}{}{}
        \tableentry{}{\textbf{Dr. Mahdi Davarpanah}}{spaceafter}
        \tableentry{Position}{Assistant Professor}{}
        \tableentry{Employer}{\href{http://ece.ut.ac.ir/}{School of Electrical and Computer Engineering}}{}
        \tableentry{}{\href{https://ut.ac.ir}{\textit{University of Tehran}}}{spaceafter}
        \tableentry{Email}{\href{mailto:m.davarpanah@ut.ac.ir}{m.davarpanah@ut.ac.ir}}{}
      \end{supertabular}
  \end{paracol}
\end{document}
