\workposition{from Oct 2019}
{}
{CafeBazaar - Android Marketplace for Iranians,}
{Developer - Video on Demand}
{
  The most popular and successful android application store in Iran, with 30M of users. The company
was founded in 2012 and currently is the third most successful Iranian startup.
}
\workposition{Jun 2017 -- Feb 2018}
{}
{Wireless Communications Lab - University of Tehran}
{M.Sc. student, Research Assistant}
{
  Running a demo of ETSI MANO using Open Air Interface vEPC components as VNFs, OpenStack as VIM and OpenBaton as NFVO;
  Under supervision of \textbf{Dr. Vahid Shahmansouri}.
}
\medskip
\workposition{from Jun 2016 -- Aug 2017}
{}
{ESFA Lab - University of Tehran}
{M.Sc. student, Research Assistant}
{
  Design and development of a measurement device used to identify phase (R, S, T) of electrical system subscribers.
  In the pilot stage more than 70000 subscribers have been measured;
  Under supervision of \textbf{Dr. Mahdi Davarpanah}.
}
\medskip
\workposition{Jun 2015 -- Aug 2015}
{}
{Wireless Communications Lab - University of Tehran}
{B.Sc. student, Research Assistant}
{
  Development of a gateway software between Iotivity constrained devices and Iotivity cloud;
  Under supervision of \textbf{Dr. Vahid Shahmansouri}.
}
\medskip
\workposition{Oct 2015 -- Jan 2016}
{}
{Array Processing Lab - University of Tehran}
{B.Sc. student, Research Assistant}
{
  Implementing a wireless communication link using SDR board based on Xilinx ZYNQ 7020 and analyzing among different modulations;
  Under supervision of \textbf{Dr. Aliazam Abbasfar}.
}
